---
title: "Multiple Linear Regression on Customer Data"
author: "Insofe Lab Session"
date: "July 02 , 2017"
output:
  html_document:
    toc_depth: 3
    toc_float: yes
  pdf_document:
    toc_depth: '3'
---
```{r}
# Go through the data and understand the attributes to get the info of the variables.
```

Write a code to clear the environment if needed
```{r}
rm(list=(ls(all=TRUE)))

```

Write a code to set the working directory.
```{r }
setwd("C:\\insofe\\lab_assignments\\20170702_Batch30_CSE7302c_CustomerData_Assignment")
getwd()
```
Think and load the libraries as and when required in this place only as best practice
```{r}
library(vegan)
library(corrplot)
library(dummies)
library(MASS)
library(car)
library(DMwR)
```
Write a code to read the csv file as "data" as per required
```{r eval=TRUE }
customer_data=read.csv("20170702_Batch30_CSE7302c_CustomerData_Assignment.csv")
```
Write a code to know the names of the attributes
```{r}
names(customer_data)

```
Write a code to find the dimensions of the data
```{r}
dim(customer_data)

```

Write a code to see the head  and tail of the dataset atleast 10rows
```{r }
head(customer_data)
tail(customer_data)

```
Write a code to see the data types of the attributes 
```{r }
str(customer_data)

```
Write a code to remove the unuseful variables and store the data 
```{r }
customer_data=customer_data[,-c(1)]

```
Write a code to observe the variables and convert them into the required formats
```{r}
str(customer_data)
cus_data_cat=c("FavoriteChannelOfTransaction","FavoriteGame")

customer_data[,cus_data_cat]=data.frame(apply(customer_data[,cus_data_cat],2,function(x) as.factor(as.character(x))))
  
```
Check the changes again using str() command
```{r }
str(customer_data)
names(customer_data)

```
Write a Code to seperate the target
```{r}
customer_data_sep_target=customer_data[,-c(13)]
names(customer_data_sep_target)

```
Write a code to get the numerical attributes out and store them as data_num
```{r }

cus_data_num=c(setdiff(names(customer_data_sep_target),cus_data_cat))


```
Perform binning on city,No of Children, Minimum age of the child,Maximum age of the child
```{r}
customer_num = customer_data_sep_target[cus_data_num]
customer_cat = customer_data_sep_target[cus_data_cat]

#library(infotheo)

#customer_num[,1]<- discretize(customer_num[,1], disc="equalfreq",nbins=2)
#customer_num[,2]<- discretize(customer_num[,2], disc="equalfreq",nbins=3)
#customer_num[,3]<- discretize(customer_num[,3], disc="equalfreq",nbins=3)
#customer_num[,4]<- discretize(customer_num[,4], disc="equalfreq",nbins=3)

head(customer_num)
tail(customer_num)
```
Write a code for Normalizing the data_num
```{r}


#customer_num_standardized <- decostand(customer_num,"standardize") # Using Z score method
#summary(customer_num_standardized)

```
Write a code to observe the correlation between the  attributes 
```{r}
customer_num_final = cbind(customer_num,TotalRevenueGenerated=customer_data[,c(13)])
cor(customer_num_final)

```
Write a code to plot the corrplot of correlation between the attributes
```{r}

corrplot(cor(customer_num_final), method = "number")
names(customer_num_final)

```
Write a code to seperate the categorical attributes
```{r}
print("Done already")

```
Write a code to combine the numerical,categorical data along with the target 
```{r}

customer_num_final_with_cat = cbind(customer_num_final,customer_cat)
names(customer_num_final_with_cat)

```
Create Dummy variables for FavoriteChannelOfTransaction and FavoriteGame

```{r}
#table(customer_num_final_with_cat_target$FavoriteChannelOfTransaction,customer_num_final_with_cat_target$FavoriteGame)

#df_final_dummy1<-dummy(customer_num_final_with_cat_target$FavoriteChannelOfTransaction)
#colnames(df_final_dummy1)=c("FavoriteChannelOfTransaction1","FavoriteChannelOfTransaction2")

#customer_num_final_dum1 <- data.frame(customer_num_final_with_cat_target,df_final_dummy1)
#names(customer_num_final_dum1)


#df_final_dummy2<-dummy(customer_num_final_with_cat_target$FavoriteGame)
#colnames(df_final_dummy2)=c("FavoriteGame1","FavoriteGame2","FavoriteGame3")
#customer_num_final_dum2 <- data.frame(customer_num_final_dum1,df_final_dummy2)
#names(customer_num_final_dum2)

#customer_num_final_with_cat=customer_num_final_with_cat[,-c(10)]
#names(customer_num_final_with_cat)

```
Check for NA values
```{r}

sum(is.na(customer_num_final_with_cat))

```


Write a code to set the seed and comment why it is used.

   **Ans** Set seed is used so that we get a random data set that is reproducible. 
```{r}

set.seed(123)

```
Write a code to get the train rows using sample 
```{r}

train_rows <- sample(x = 1:nrow(customer_num_final_with_cat), size = 0.7*nrow(customer_num_final_with_cat))

```
Write a code to get the train and test 
```{r}
train_data <- customer_num_final_with_cat[train_rows, ]

test_data <- customer_num_final_with_cat[-train_rows, ]

head(train_data)
head(test_data)
#plot(customer_num_final_dum$TotalRevenueGenerated, customer_num_final_dum$NoOfChildren, xlab = #"TotalRevenueGenerated", ylab = "NoOfChildren", main = "TotalRevenueGenerated vs NoOfChildren")

```
Write a code to form a linear regression model 
```{r}
model_basic <- lm(formula = TotalRevenueGenerated~. , data = train_data)
model_basic
```
Write a code to plot the model
```{r}

par(mfrow = c(2,2))

plot(model_basic)

```
Write a code to check the summary of the model 
```{r}

summary(model_basic)

```
Write a code to predict the value of the target on the linear model 
```{r}

preds_model_basic <- predict(model_basic, test_data[, !(names(test_data) %in% c("TotalRevenueGenerated"))])
preds_model_basic
```
Write a code to use stepAIC
```{r}

model_aic <- stepAIC(model_basic, direction = "both")

summary(model_aic)

```
Write a code to predict it on stepAIC
```{r}
preds_model_aic <- predict(model_aic, test_data[, !(names(test_data) %in% c("TotalRevenueGenerated"))])
preds_model_aic
```
Write a code to check the multicollinearity in the lm model 
```{r}

vif(model_basic)

```
Write a code to check the plots of the models
```{r}

par(mfrow = c(2,2))

plot(model_aic)

```

Write a code to check the multicollinearity problem
```{r}

vif(model_aic)


```
Write a code to evaluate the error in the prediction of AIC

```{r}


regr.eval(test_data$TotalRevenueGenerated, preds_model_aic)
```
Write a code to evaluate the error on the prediction of Linear Regression
```{r}


regr.eval(test_data$TotalRevenueGenerated, preds_model_basic)
```





